Fluid structure interaction and rigid fluid coupling in SPH

### 2020-08-01 manuscript/paper.tex
2d rigid body algorithm implemented. Memory pointer issues. Not working

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[utf8]{inputenc}

% For the TODOs
\usepackage{xcolor}
\usepackage{xargs}
\usepackage[colorinlistoftodos,textsize=footnotesize]{todonotes}
\usepackage{lineno}

%% Our macros
\input{macros.tex}

@@

  \title{Comparison of SPH schemes for solid mechanics}
  \author[IITB]{A Dinesh\corrcoef{cor1}}
  \ead{adepu.dinesh.a@gmail.com}
  \author[IITB]{Prabhu Ramachandran}
  \ead{prabhu@aero.iitb.ac.in}
\address[IITB]{Department of Aerospace Engineering, Indian Institute of
  Technology Bombay, Powai, Mumbai 400076}

@@

\begin{abstract}
  XXX
  \end{abstract}

@@

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{cleveref}

% For the TODOs
\usepackage{xcolor}
\usepackage{xargs}
\usepackage[colorinlistoftodos,textsize=footnotesize]{todonotes}
\newcommand{\todoin}{\todo[inline]}
% from here: https://tex.stackexchange.com/questions/9796/how-to-add-todo-notes
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}

%Boldtype for greek symbols
\newcommand{\teng}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\ten}[1]{\ensuremath{\mathbf{#1}}}

\usepackage{lineno}

@@

  \title{Fluid structure interaction and rigid fluid coupling in SPH}
  \author[IITB]{A Dinesh\corref{cor1}}
  \ead{adepu.dinesh.a@gmail.com}
  \author[IITB]{Prabhu Ramachandran}
  \ead{prabhu@aero.iitb.ac.in}
  \address[IITB]{Department of Aerospace Engineering, Indian Institute of
    Technology Bombay, Powai, Mumbai 400076}

@@

\begin{abstract}
\end{abstract}

@@

\section{2D Rigid body dynamics}
\label{sec:rb-2d}

\subsection{Center of mass, Linear momentum of a rigid body}
\label{sec:center-mass}

Let $N$ be an inertial frame in which a body $B$ is situated and is
discretized into finite number of points. The center of mass is defined as \cite{rao2006dynamics}

\begin{equation}
  \label{eq:center-of-mass}
  \ten{r}_{cm} = \frac{\sum_i m_i \; \ten{r}_i}{M}
\end{equation}

\noindent where $\ten{r}$ is the position vector of the point $i$ with mass
$m_i$ in inertial frame $N$ and $M$ is the total mass of the rigid body under
consideration.

The linear momentum of the rigid body in the inertial frame is

\begin{equation}
  \label{eq:lin-mom-of-rigid-body}
  \ten{G} = \sum_i m_i \; \ten{v}_i
\end{equation}

\begin{equation}
  \label{eq:center-of-mass-velocity}
  \ten{v}_{cm} = \frac{\sum_i m_i \; \ten{v}_i}{M}
\end{equation}

\noindent where $\ten{v}$ is the velocity vector of the point mass $i$ as
observed in the inertial frame. Similarly the acceleration of the center of
mass is

\begin{equation}
  \label{eq:acceleration-of-rigid-body}
  \ten{a}_{cm} = \frac{\sum_i m_i \; \ten{a}_i}{M}
\end{equation}
